Choose a License

### 2024-09-09 choose_license.qmd
Fix code

```r
direct_deps <- unique(renv::dependencies()$Package)
all_deps <- tools::package_dependencies(
  packages = direct_deps,
  which = "strong",
  recursive = TRUE
) |>
  unlist() |>
  append(deps) |>
  unique()
unique(installed.packages(fields = "License")[pkgs, "License"])
```
:::

>>>>

```r
direct_deps <- unique(renv::dependencies()$Package)
all_deps <- tools::package_dependencies(
  packages = direct_deps,
  which = "strong",
  recursive = TRUE
) |>
  unlist() |>
  append(direct_deps) |>
  unique()
unique(installed.packages(fields = "License")[all_deps, "License"])
```
:::
